Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-11-19 paper/results.tex
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@669 3fc257bb-8550-0410-81b3-a5c103da83f7

@@

Figure~\ref{f:prbig}, shows the performance of the various PageRank
implementations on distributed memory and multi-threaded
architectures.  The MR-MPI and Trilinos implementations are described
in Sections~\ref{subsec:graph_pagerank}
and~\ref{subsec:results_pagerank}, respectively.  In the
multi-threaded MTGL implementation, rank propagates via adjacency list
traversal in a compressed sparse-row data structure.  To maintain its
scalability, code must be written so that a single thread spawns the
loop that processes all in-neighbors of a given vertex; this detail
enables the compiler to generate hotspot-free code.

>>>>

\subsection{Implementation effort}

To give a rough sense of the effort involved to implement the various
MapReduce algorithms described in this section, we list the line
counts of the C++ codes used to perform the benchmarks.  Each code
makes calls to the MR-MPI library and implements the algorithm in the
indicated figure.  The line counts exclude comments and blank lines
which typically add about 30\% to the total.  They also exclude the
routines used to generate the R-MAT matrix input (except in the case
of the two R-MAT algorithms themselves) or process it into
upper-triangular form, since that is common to several of the
benchmarks.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT & PageRank & Tri & CC & MIS & SSSP & SSSP \\
\hline
Line count & 208 & 216 & 694 & 367 & 453 & 393 & 505 & 569 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Line counts of codes that implement each of the graph
  algorithms in the associated figures.}
\label{t:rmat}
\end{center}
\end{table}

For comparison, we wrote a parallel distributed-memory R-MAT
generation code with explicit MPI calls using a different
(non-MapReduce) algorithm than that of Figures \ref{fig:rmat} and
\ref{fig:rmat2}.  It required 1842 lines of code, mainly because it
must implement the parallelism explicitly whereas the codes of this
section relegate that task to the MR-MPI library.  Our collaborators
(see Acknowledgements) have a Hadoop implementation of the SSSP
algorithm of Figure \ref{fig:sssp}.  It required XXX lines of Java
code.

@@

Figure~\ref{f:prbig} shows the performance of the various PageRank
implementations on distributed memory and multi-threaded
architectures.  The MR-MPI and Trilinos implementations are described
in Sections~\ref{subsec:graph_pagerank}
and~\ref{subsec:results_pagerank}, respectively.  In the
multi-threaded MTGL implementation, rank propagates via adjacency list
traversal in a compressed sparse-row data structure.  To maintain its
scalability, code must be written so that a single thread spawns the
loop that processes all in-neighbors of a given vertex; this detail
enables the compiler to generate hotspot-free code.
